Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-03-17 icmssp-paper/icmssp2019-sigconf.tex
Rewrite Chapter 1 for conference paper

\begin{abstract}
Homomorphic cryptography allows for encrypted data to be modified and operated on without requiring decryption, although current homomorphic cryptosystems are either limited in their permitted operations or are significantly more time-intensive than standard non-homomorphic cryptosystems. Regardless, homomorphic cryptography has been targeted for use in secure image processing and facial recognition, due to their ability to maintain data privacy. In this paper, we compared the viability of the Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems for facial image processing applications, by implementing a software library equipped with these cryptosystems, and comparing their time efficiency and accuracy. Furthermore, as an extension to previous research, we attempt to support non-linear image processing operations. Preliminary results have shown that the Paillier and DGK cryptosystems are comparable in accuracy and may be used for image negation, but only the Paillier cryptosystem is consistent enough to produce reasonable to accurate results.
\end{abstract}

>>>>

\begin{abstract}
\input{parts/00_abstract.tex}
\end{abstract}

### 2019-03-17 icmssp-paper/parts/01_introduction.tex
Rewrite Chapter 1 for conference paper

\section{Introduction}
% \subsection{Context of the Study}
% Digital data privacy and security is a growing concern in various fields, such as cloud computing~\cite{potey_homomorphic_2016}, health information systems~\cite{kester_cryptographic_2015}, and video surveillance~\cite{upmanyu_efficient_2009}. 
Digital image encryption is a growing concern today, with many algorithms existing in the literature~\cite{murugan_survey_2018}.

% TODO : Mention the four HE schemes here
Of particular interest is homomorphic encryption, where operations such as addition and multiplication can be performed on encrypted data. These operations are then preserved when the data is decrypted. In this manner, data is manipulated without compromising data privacy, as the encrypted data being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}. In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations on the encrypted data such as image adjustment, filtering, and morphological/feature extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. More advanced operations have also been implemented using homomorphic cryptosystems, such as facial recognition \cite{hutchison_privacy-preserving_2009} and neural networks \cite{hesamifard_cryptodl:_2017}. This study in particular focuses on facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems with regard to image processing on faces.
% Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

% TODO: be specific here, integrate objectives and scope
% Focus objectives on new developments
In this study, we accomplish the following:
\begin{enumerate}
    \item Implement common linear and non-linear image processing operations using the Paillier, DGK, DGHV, and BGV homomorphic encryption schemes.
    \item Compare the time efficiency and accuracy of common image processing operations under these homomorphic encryption schemes, and of common image processing operations without using homomorphic encryption;
    \item Create a library to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
For this study, we adopted the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
    \item Mean Squared Error (MSE)
    \item Peak Signal to Noise Ratio (PSNR)
    \item Structural Similarity Index (SSIM)
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed

@@

% TODO: shorten this
% \subsection{Significance of the Study}
This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial recognition and detection.

We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms. Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.

>>>>

\section{Introduction}
Digital image security is a growing concern, and various image encryption schemes have been developed and analyzed in the literature~\cite{murugan_survey_2018, kester_cryptographic_2015, jain_image_2016, singh_image_2015, khoirom_cryptanalysis_2018}. Cryptosystems allow for the secure transmission of data by way of encryption and decryption schemes. 
Of particular interest is homomorphic image encryption, which allows operations to be performed on encrypted images. These operations are then preserved when the images is decrypted. In this manner, images are manipulated without compromising data privacy, as the image being operated on remains secure~\cite{fontaine_survey_2007, sen_homomorphic_2013}.

In the area of homomorphic image encryption, there is interest in being able to perform image manipulation operations such as image adjustment, image filtering, and morphological extraction operations~\cite{ziad_cryptoimg:_2016, gonzalez_digital_2008}. The \textit{CryptoImg} software library implements common linear operations on encrypted images~\cite{ziad_cryptoimg:_2016}. There is also work on facial recognition on encrypted images\cite{turk_eigenfaces_1991, hutchison_privacy-preserving_2009}. However, preprocessing which requires non-linear operations, such as those in~\cite{oravec_illumination_2010}, has yet to be performed in the encrypted domain.

Homomorphic encryption schemes have two main limitations: first, they are limited in the operations that can be performed on encrypted data efficiently~\cite{li_elliptic_2012}, and second, they are slower than non-homomorphic schemes~\cite{sen_homomorphic_2013}. This paper presents implementations of non-linear image operations under a homomorphic encryption scheme, and evaluates their applicability and performance.

To investigate the applicability of homomorphic image manipulation, in Section \ref{sec:chapter_2}, we introduce three homomorphic cryptosystems prominent in the literature: Paillier, Damg{\aa}rd--Geisler--Kr{\o}igaard (DGK), and Brakerski--Gentry--Vaikuntanathan (BGV) cryptosystems. We list important properties of each cryptosystem and show how they can be used for non-linear image processing operations, compared to previous uses in the literature. In Section \ref{sec:chapter_3}, we implement a software library allowing for common linear and non-linear image processing operations using each of the three cryptosystems, assuming a client-server model for secure computation.

To evaluate the performance of homomorphic image manipulation, in Section \ref{sec:chapter_4}, we test the time efficiency and accuracy of common image processing operations under homomorphic encryption. We test for image quality of the resulting images using Mean Squared Error (MSE), Peak Signal to Noise Ratio (PSNR), and Structural Similarity Index (SSIM), which are measures of image quality used for assessing image encryption schemes~\cite{ahmed_benchmark_2016}.

@@

% \subsection{Significance of the Study}
% This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial recognition and detection.

% We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms. Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.

### 2019-03-17 icmssp-paper/parts/03_methodology.tex
Rewrite Chapter 1 for conference paper

\section{Methodology}
We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications. In particular, the study consists of the following:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
\end{itemize}

>>>>

\section{Methodology}
\label{sec:chapter_3}
We apply three homomorphic encryption schemes~\cite{ziad_cryptoimg:_2016, pieprzyk_efficient_2007, garay_algorithms_2014} for use in image processing and facial recognition applications. In particular, the study consists of the following:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
\end{itemize}
